Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-03 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
file of time fixed in chunk 6

```{r Simulated_comparative_time2, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 1000
mu <- 1
B <- 40#100

sample.size <- c(25,49, 81, 121)
L_values <- c( 2, 8)

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
)

all_TestStatistics <- list()

execution_times <- list()

for (estimator_name in names(bootstrap_estimators)) {

  TestStatistics <- list()

@@

save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")
```

```{r Table_statistic_time2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_data_time2.Rdata")

>>>>

```{r Simulated_comparative_time3, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
R <- 1000
mu <- 1
B <- 40

sample.size <- c(25,49, 81, 121)
L_values <- c(2, 8)

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
)
if (!file.exists("./Data/results_data_time_3.Rdata")) {#Deactivate this line to regenerate the file
  set.seed(1234567890, kind = "Mersenne-Twister")

  all_TestStatistics <- list()
  execution_times <- list()

  for (estimator_name in names(bootstrap_estimators)) {
    TestStatistics <- list()

@@

  save(all_TestStatistics, execution_times, file = "./Data/results_data_time_3.Rdata")
}

```{r Table_statistic_time3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_data_time_3.Rdata")
